Meta-analysis

### 2020-07-01 04_MetaAnalysis.Rmd
Save contrasts data into file for manuscript Add here() as a library for interoperability additional description to log ratio test of models

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               lme4,
               RColorBrewer,
               metafor,
               netmeta)

@@

AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
anova(PM_mv, PM_mv_St1) # PM_mv is the better model
```

@@

@@

data.frame(
   contrasts = change_labels(meta_cont$hyp[, 1]),
   estimates = meta_cont$Lb,
   se = meta_cont$se,
   z_val = meta_cont$zval,
   pval = meta_cont$pval,
   VisP = p_star(meta_cont$pval)
)
```

>>>>

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               lme4,
               RColorBrewer,
               metafor,
               here,
               netmeta)

@@

AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
anova(PM_mv, PM_mv_St) # PM_mv is the better model
AIC(PM_mv_St)
anova(PM_mv_St, PM_mv_St1) # PM_mv_St is the better model
```

@@

I have also tested the structure for testing the random trial and spray_management variables, these show that there is no significant difference to the models `PM_mv_St` and `PM_mv_St1` and that the originally method of specifying the random variables within the `trial` factor provides us with the best model.

@@

table3 <- data.frame(
   contrasts = change_labels(meta_cont$hyp[, 1]),
   estimates = meta_cont$Lb,
   se = meta_cont$se,
   z_val = meta_cont$zval,
   pval = meta_cont$pval,
   VisP = p_star(meta_cont$pval)
)
write.csv(table3, here("cache/Table3_contrasts.csv"), row.names = FALSE)
```
